Multisensor Architecture for an Intersection Management System

### 2015-06-10 ch2-mdf_ims.tex
IMS Review table updated and moved to an independent file.

In the next table is presented a compilation of several developments within IMS field. For each work a brief overview and a remark of how each component is related to it are given.

@@

On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places, for drivers and authorities too. There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and many topics involved have been proposed through the years. To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed.
%\end{document}

>>>>

In the table \ref{reviewtable} is presented a compilation of several developments within IMS field. For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it. Target and implementation components could be infered from the comment.

\input{extra/ims_review_table}

@@

On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places for drivers and for authorities too. There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and with many topics involved have been proposed through the years. To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed, and a review of developments in Intersection Management Systems is presented.

%\end{document}
